---
title: "Statistics: Chi-squared"
author: "Scott Schumacker"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This project will show an example chi-squared analysis on example data testing for any association between maximum education level and salary.

***Loading Packages***
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(tidyr)
```

## Creating a data set
```{r}
Education_Level = c(rep("GED",50), rep("Undergraduate",50), rep("Graduate",50))
Salary = c(rep("Under 75K", 45), rep("Over 75K", 5), rep("Under 75K",20), rep("Over 75K",30), rep("Under 75K", 2), rep("Over 75K",48))
df = data.frame(Education_Level, Salary)
dftable <- table(df)
print(dftable)
```

### Statistical Analysis

Before running the chi-squared test we need to specify our hypothesis:
H0: There is no association between the variables (null hypothesis)
Ha: There is an association between the variables (alternative hypothesis)

We can set our alpha to 0.05 for this example. This means that we are looking for a p-value below 0.05 to reject the null hypothesis.

***Chi-square Test***
```{r}
print(chisq.test(dftable))
```
### Results

Our p-value is less than 0.01 which means that we can reject our null hypothesis. We can assume that there is a statistically significant association between maximum education level and either making over $75,000 or under $75,000.
